---
title: "Assignment V"
subtitle: "GitHub and the ticketmaster.com API"
author: "Isabell Goebel (Student ID: 5374775)"
output: 
  html_document:
     theme: lumen
     highlight: haddock
     code_download: true  # download button for code (upper right corner)
     toc: true  # table of contents with links
     toc_depth: 3  # depth of toc, i.e. subchapters
     toc_float:  # toc on the left (always visible, also when scrolling)
        collapsed: false  # otherwise not full toc (subchapters) shown
     number_sections: true  # numbers sections
runtime: shiny
---

<br>

R Version: `r version$version.string`  
Last updated: `r Sys.time()`

<br>

I worked with no one. I hereby assure that my submission is in line with the 
*Code of Conduct* outlined on the lecture slides.

------------------------

<details><summary>Task</summary>

In this assignment, you will apply what you have learned about APIs and about 
version control with Git(Hub).
First, you will acquire data about event venues using the API provided by ticketmaster.com. 
You will then use the geospatial data to visualize the extracted data on a map. 
Finally, you will repeat the same steps for a different country. 
It is further required that the entire project and its version history is documented 
in your personal GitHub repository.

1. Setting up a new GitHub repository

* Register on github.com in case you have not done this already.
* Initialize a new public repository for this assignment on GitHub.
* For the following exercises of this assignment, follow the standard Git workflow 
  (i.e., pull the latest version of the project to your local computer, then stage, 
  commit, and push all the modifications that you make throughout the project). 
  Every logical programming step should be well documented on GitHub with a meaningful 
  commit message, so that other people (e.g., your course instructor) can follow 
  understand the development history. 
  You can to do this either using Shell commands or a Git GUI of your choice.
* In the HTML file that you submit, include the hyperlink to the project repository 
  (e.g., https://github.com/yourUserName/yourProjectName)
  

2. Getting to know the API

* Visit the documentation website for the API provided by ticketmaster.com
* Familiarize yourself with the features and functionalities of the Ticketmaster 
  Discovery API. 
  Have a particular look at rate limits.
* Whithin the scope of this assignment, you do not have to request your own API key. 
  Instead retrieve a valid key from the API Explorer. 
  This API key enables you to perform the GET requests needed throughout this assignment.
* Even though this API key is not secret per se (it is publicly visible on the 
  API Explorer website), please comply to the common secrecy practices discussed 
  in the lecture and the tutorial: Treat the API key as a secret token. 
  Your API key I key should neither appear in the code that you are submitting 
  nor in your public GitHub repository.


3. Interacting with the API - the basics

* Load the packages needed to interact with APIs using R.
* Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). 
  Extract the content from the response object and inspect the resulting list. 
  Describe what you can see.
* Extract the name, the city, the postalCode and address, as well as the url 
  and the longitude and latitude of the venues to a data frame.
  
 
</details>  

------------------------


```{r preamble, message = FALSE}
# clear current workspace
remove(list = ls())
# directory
#main<-file.path("/Users/isabellheinemann/Documents/UniTübingen/2020/0_DataScienceProject/assignments/assignment4")
```


<details><summary>Chunk Options / Directory</summary>

```{r setup}
# global code chunk options
knitr::opts_chunk$set(echo=TRUE,  # display code
                      options(width=80),  # line length 80 characters
                      tidy=TRUE, tidy.opts=list(width.cutoff=80),  # tidy code
                      # set directory
                      root.dir="/Users/isabellheinemann/Desktop/AssignmentV")
```

</details>


<details><summary>Packages and Libraries</summary>

```{r packages, message = FALSE}
# Check if packages have been installed before; if not, install them
if (!require("tidyr")) install.packages("tidyr")
if (!require("dplyr")) install.packages("dplyr")
if (!require("knitr")) install.packages("knitr")
if (!require("formatR")) install.packages("formatR")
if (!require("jsonlite")) install.packages("jsonlite")
if (!require("rvest")) install.packages("rvest")
if (!require("xml2")) install.packages("xml2")
if (!require("httr")) install.packages("httr")

# call package libraries
library(tidyr)
library(dplyr)
library(knitr)
library(formatR)
library(jsonlite)
library(rvest)
library(xml2)
library(httr)
```

</details>

------


```{r spin, echo = FALSE, results = 'hide'}
# To receive .Rmd file of this file
spin("Goebel_Isabell_AssignmentV.R", knit = FALSE)
```




# GitHub

My GitHub repository: https://github.com/IsabellGoebel/AssignmentV



# API


All API calls follow this format: 
https://app.ticketmaster.com/{package}/{version}/{resource}.json?apikey=**{API key}


**Rate Limit**

* All API keys are issued with a default quota of 5000 API calls per day and 
  rate limitation of 5 requests per second. 
* We do increase rate limits on case-by-case basis. In order to increase the 
  rate limit for a particular application, we need to verify the following:
  * The application is in compliance with our Terms of Service
  * The application is in compliance with our branding guide
  * The application is representing the Ticketmaster data properly
  
  Once these three criteria are verified, the rate limit is increased to what 
  Ticketmaster and the developer determine to be appropriate.


**Rate Limit Info in Response Header**

You can see how much of your quota has been used by checking the following response headers:

* Rate-Limit: What’s the rate limit available to you. The default is 5000.
* Rate-Limit-Available: How many requests are available to you. This will be 5000 minus all the requests you’ve done.
* Rate-Limit-Over: How many requests over your quota you’ve made.
* Rate-Limit-Reset: The UTC date and time of when your quota will be reset.
* `curl -I 'http://app.ticketmaster.com/discovery/v1/events.json?keyword=Queen&apikey=xxx'`


API Response When Quota is Reached

When you do go over your quota, you will get an HTTP status code 429 indicating 
you’ve made too many requests. 
The following is the API response you will receive:

`{
    "fault": {
         "faultstring": "Rate limit quota violation. Quota limit  exceeded. Identifier : {apikey}",
               "detail": {
                      "errorcode": "policies.ratelimit.QuotaViolation"
  }}}`


**API Explorer**

see https://developer.ticketmaster.com/api-explorer/v2/

Source key from file key.R into this file

```{r }
source("key.R")
```




# Interacting with the API - the basics


* Load the packages needed to interact with APIs using R: see preamble

* Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). 
  Extract the content from the response object and inspect the resulting list. 
  Describe what you can see.

```{r }
# since the country will vary
country <- "DE"



# delete this later!!!
key <- "7elxdku9GGG5k8j0Xm8KWdANDgecHMV0"



# generate response object
ticketmaster <- GET("https://app.ticketmaster.com/discovery/v2/events",
                    query = list(apikey = key,
                                 countryCode = country)) #%>% content()

# show content & status code of object
ticketmaster

# extract content of response object
content <- jsonlite::fromJSON(content(ticketmaster, as="text"))

# inspect content
glimpse(content)

# event content
df <- data.frame(content$'_embedded'$events)
glimpse(df)
```


The extracted (large) list consist of 3 elements.
In `_embedded$events` there is a data frame consisting of 20 observations of 16
variables.
Further, `_links` contains links to the first, next, and last page found on the
main page "/discovery/v2/events", from where I extracted the data.
Lastly, `page` contains information on the size (20), total elements (1590), 
total pages (80) and number (0) of the extracted data. 


```{r }
# generate response object
ticketmaster2 <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = key,
                                 countryCode = country)) #%>% content()

# show content & status code of object
ticketmaster2

# extract content of response object
venuesDE <- jsonlite::fromJSON(content(ticketmaster2, as="text"))

# inspect content
glimpse(venuesDE)
```


The extracted list consist of 3 elements.
In `_embedded$venues` there is a data frame consisting of 20 rows of 19 columns.
Further, `_links` contains links to the first, next, and last page found on the
main page "/discovery/v2/venues.json", from where I extracted the data.
Lastly, `page` contains information on the size (20), total elements (4743), 
total pages (238) and number (0) of the extracted data. 



* Extract the name, the city, the postalCode and address, as well as the url 
  and the longitude and latitude of the venues to a data frame.


```{r }
# venue content
venue_df <- data.frame(venuesDE$'_embedded'$venues)
glimpse(venue_df)

# extract variables from data frame 'venue_df'
vars <- c("name", "postalCode", "url")

# combine in new data frame 'venue_data'
venue_data <- data.frame(venue_df[vars])

# add variables from data frame within data frame 'venue_df'
venue_data$city = venue_df[["city"]][["name"]]
venue_data$address = venue_df[["address"]][["line1"]]
venue_data$longitude = venue_df[["location"]][["longitude"]]
venue_data$latitude = venue_df[["location"]][["latitude"]]

# adjust order
order <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")
venue_data <- venue_data[, order]

# check new data frame
glimpse(venue_data)
```



ISSUE: longi and lati only have 2 entries?




# Interacting with the API - advanced

* Have a closer look at the list element named page. 
  Did your GET request from exercise 3 return all event locations in Germany? 
  Obviously not - there are of course much more venues in Germany than those 
  contained in this list. 
  Your GET request only yielded the first results page containing the first 20 
  out of several thousands of venues.
  
* Check the API documentation under the section Venue Search. 
  How can you request the venues from the remaining results pages?
  
* Write a for loop that iterates through the results pages and performs a GET 
  request for all venues in Germany. 
  After each iteration, extract the seven variables name, city, postalCode, 
  address, url, longitude, and latitude. 
  Join the information in one large data frame.
  
* The resulting data frame should look something like this (note that the exact 
  number of search results may have changed since this document has been last modified):









<br><br>

<a href="#top">Back to top</a>
